A High-Order Discontinuous Galerkin Solver with Dynamic Adaptive Mesh Refinement to Simulate Cloud Formation Processes

### 2019-05-03 writing/paper/paper.tex
Small detail fixes.

\begin{figure}[tb]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics{paper_lid_driven_cavity}
    \caption{\label{fig:cavity-flow}Our approximation (solid lines) of the lid-driven cavity flow vs.\ reference solution (crosses) of~\cite{ghia1982high}.}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics{paper_taylor_green_vel}
    \caption{\label{fig:taylor-green}Taylor green, velocity slices.}

@@

\begin{figure}[tb]
\centering
\begin{minipage}{.5\textwidth}
  \centering
    \includegraphics{paper_abc_flow_velocity}
    \captionof{figure}{\label{fig:abc-flow}Our approximation (markers) of the \textsc{abc}-flow vs.\ analytical solution (lines, \cref{eq:abc-flow}).
    All other axes are held constant at a value of 0.}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
    \includegraphics[width=\textwidth]{paper_two_bubbles_fv}
    \captionof{figure}{\label{fig:two-bubbles-fv}%
    Colliding bubbles with \muscl{}}
\end{minipage}
\end{figure}

@@

In addition, we simulated the same scenario with our \muscl{} method, using $3^2$ patches with $80^2$ finite volume cells each\todo{check}.
As we use limiting, we do not need any viscosity.
The results of this method (\cref{fig:two-bubbles-fv}) also agree with the reference but contain fewer details.
Note that the numerical dissipativity of the finite volume scheme has a smoothing effect that is similar to the smoothing caused by viscosity.

>>>>

\begin{figure}[tb]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics{paper_lid_driven_cavity}
    \caption{\label{fig:cavity-flow}Our approximation (solid lines) of the lid-driven cavity flow vs.\ reference solution (crosses) of~\cite{ghia1982high}.}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics{paper_taylor_green_vel}
    \caption{\label{fig:taylor-green}Our result (markers) of the Taylor-Green vortex vs.\ the analytical solution (lines) \cref{eq:taylor-green}.
    The plot shows two velocity slices, the respective other coordinate is held constant at a value of $\pi$.}

@@

\begin{figure}[tb]
\centering
% or .473 size each, and \\quad inbetween
\begin{minipage}{.5\textwidth}
  \centering
    \includegraphics{paper_abc_flow_velocity}
    \captionof{figure}{\label{fig:abc-flow}Our approximation (markers) of the \textsc{abc}-flow vs.\ analytical solution (lines, \cref{eq:abc-flow}).
    All other axes are held constant at a value of 0. We show every 6th value.}
\end{minipage}~%
\begin{minipage}{.5\textwidth}
  \centering
    \includegraphics[width=\textwidth]{paper_two_bubbles_fv}
    \captionof{figure}{\label{fig:two-bubbles-fv}%
    Colliding bubbles with \muscl{}}
\end{minipage}
\end{figure}

@@

In addition, we simulated the same scenario with our \muscl{} method, using $7^2$ patches with $90^2$ finite volume cells each.
As we use limiting, we do not need any viscosity.
The results of this method (\cref{fig:two-bubbles-fv}) also agree with the reference but contain fewer details.
Note that the numerical dissipativity of the finite volume scheme has a smoothing effect that is similar to the smoothing caused by viscosity.
